\documentclass{resume} \usepackage{url} \usepackage[pdfborderstyle={/W
0}]{hyperref}

%
% set the space used for category titles here: use the same value for
% oddsidemargin and marginparwidth [the latter will be reset to account for
% marginparsep]
% 
\setlength{\oddsidemargin}{1in} \setlength{\marginparwidth}{1in}

% 
% calculate other dimensions [textwidth and evensidemargin] in function of
% oddsidemargin and marginparwidth: would be nicer to put in the class file...
%
\addtolength{\marginparwidth}{-\marginparsep}
\setlength{\evensidemargin}{\oddsidemargin} \setlength{\textwidth}{\paperwidth}
\addtolength{\textwidth}{-2in} \addtolength{\textwidth}{-2\oddsidemargin}
\addtolength{\textwidth}{\marginparwidth}
\addtolength{\textwidth}{\marginparsep}

%
\setlength{\topmargin}{-1in}

%
\renewcommand{\titlenamefont}{\bf\Large} \renewcommand{\categoryfont}{\sc}
\renewcommand{\labelcitem}{}

%\newcommand{\period}{\hspace{-0.35em}, \small\sl}
\newcommand{\period}{\hfill\small\sl} \newcommand{\teamsize}{\sc\footnotesize
Team Size: }


\author{Siddhartha Reddy Kothakapu}


% - Address --------------------------------------------------------
\address { \url{http://www.grok.in/}\\ \url{http://www.linkedin.com/in/sidsr} }
{ \href{mailto:sids@grok.in}{sids@grok.in}\\ +91 998 028 7437 }


\begin{document} \maketitle

% - Education ---------------------------------------------------
\begin{category}{Education}

    \citem{M.Tech in Information Technology} {\footnotesize(3.71 CGPA)}
    {\period Jun 2006} \begin{quote} International Institute of Information
        Technology, Bangalore \end{quote}

\end{category}


% - Experience --------------------------------------------------
\begin{category}{Experience}

    \citem{Senior/ Software Engineer,} Ziva Software, Bangalore {\period Jul
    2006 - Nov 2007} \begin{quotation} {\em Ziva Software Pvt Ltd} is a Venture
        Capital funded startup based out of Bangalore, India providing products
        and services in the {\em Mobile Search} domain. Established in late
        2005, Ziva has provided search solutions to different players in the
        mobile industry including operators and content owners. In 2007, Ziva
        launched {\em Zook}, it's consumer facing mobile search system.

        Was the first non-founding employee to join the company. Have been core
        member of the team, involved in most of the projects and actively
        participated in defining the development roadmap for them. % ``for
        them'' or ``for the company''?  \end{quotation}

\end{category}


% -Publications ------------------------------------------ %
\begin{category}{Publication}

    \citemnobullet {\bf Measures of ``Ignorance'' on the Web} {\period Dec
    2006} \begin{quote} International Conference on Management of Data, Delhi,
        India \end{quote}

\end{category}


% - Projects ---------------------------------------------------
\begin{category}{Selected Projects}

    \citem{Buddhi Online,} Ziva Software, Bangalore; {\teamsize 1} {\period Nov
    2007 - Present} \begin{quotation} Prototype of a system to fetch {\em
        Yahoo! BOSS} Web search results at run time, fetch the web pages in the
        results and extract {\em snippets} that can possibly provide an answer
        to the query right away.  \end{quotation}

    \citem{Buddhi,} Ziva Software, Bangalore; {\teamsize 2-3} {\period Apr 2007
    - Present} \begin{quotation} A dream to crawl the Web and automagically
        extract {\em information content entities} off the crawled pages.

        \begin{itemize} \item Designed and implemented \begin{itemize} \item a
                {\em Focused Crawler} based on the {\em Nutch} open source
                crawler.  \item a {\em HTML reducer} that transforms complex
                HTML pages into minimal HTML for easier analysis.  \item a {\em
                page abstractor} that discerns logical structures (such as
                tables, lists etc.) from unstructured HTML.  \end{itemize}
            \item Set up the {\em Hadoop} based infrastructure for the crawling
                and extraction.  This was initially set up on a cluster of {\em
                Amazon EC2} machines with {\em Amazon S3} as a data store.
        \end{itemize} \end{quotation}

    \citem{Zook,} Ziva Software, Bangalore; {\teamsize 2-3} {\period Jan 2007 -
    Present} \begin{quotation} Ziva Software's flagship mobile search engine.
        The main promise is to provide exact answers to questions in the least
        number of clicks; implying that the search engine provides information
        right away rather than directing the user to another website that {\em
        might} have the information.

        \begin{itemize} \item Set up the search system infrastructure.  \item
                Designed the {\em User Experience} and {\em User Interface} of
                the WAP and SMS interfaces.  \item Responsible for deploying
                releases.  \item Created a HTTP based API for accessing the
                search system.  \end{itemize} \end{quotation}

    \citem{Zivabot,} Ziva Software, Bangalore {\teamsize 1} {\period Aug 2006 -
    Oct 2006} \begin{quotation} A scalable, highly-configurable, generic
        scraping system for crawling specific websites containing useful
        information and extracting that information.

        Was fully responsible for the design and implementation of the system.
        Configured the system and set it up to work with an initial set of
        websites which provided base content for the Zook mobile search engine.
    \end{quotation}

    \citem{Better Web Buys;} {\teamsize 2} {\period Feb 2006 - May 2006}
    \begin{quotation} A {\em faceted price comparison shopping search engine}
        with over 20 million items across more than 100 merchants.

        Was completely responsible for the whole project right from downloading
        feeds, parsing them, storing them in a database, indexing, searching,
        user experience and setting up the entire system on a cluster of
        machines. Used {\em Sphynx} as the backend search system.
    \end{quotation}

    \citem{yadb -- Yet Another DataBase,} IIIT, Bangalore; {\teamsize 3}
    {\period Aug 2005 - Dec 2005} \begin{quotation} A reasonably {\em complete
        RDBMS} with a buffered memory manager, B+ tree indexing and a complete
        database management module including support for basic SQL, table
        management, paged storage etc. Part of the {\em Advanced Databases}
        course.  \end{quotation}

    \citem{Top News,} IIIT, Bangalore; {\teamsize 1} {\period Sep 2005 - Oct
    2005} \begin{quotation} A system to bring out the top news of the hour by
        clustering the news items obtained from the feeds provided by several
        news sources. Any news being discussed by multiple sources within a
        given (variable) timeframe is marked as top news. A bi-partite graph
        based clustering algorithm was used for clustering based on just the
        title and summary of the news item. {\em Part of the Web Information
        Retreival} course.  \end{quotation}

    \citem{SOS -- S Operating System;} {\teamsize 2} {\period Sep 2002 - Oct
    2003} \begin{quotation} \end{quotation}

\end{category}


% - Skills --------------------------------------------------
\begin{category}{Skills}

    \citem{Languages:} Perl, Java, C/C++, Ruby, Python

    \citem{Softwares/Frameworks:} Hadoop, Nutch, Lucene, Solr, Sphynx, WEKA,
    Ruby on Rails, Prototype, Hibernate

\end{category}


% - Intersts --------------------------------------------------
\begin{category}{Interests} \citemnobullet Information Engineering---Retrieval,
    Extraction \& Management, Scalable Architectures, Distributed \& Cloud
    Computing, Usability \& User Experience \end{category}


\renewcommand{\labelcitem}{$\diamond$}


% - Honors ---------------------------------------------------
\begin{category}{Honors} \citembullet Valedictorian for the class for 2006 at
    IIIT, Bangalore. {\period Jun 2006} \citembullet Was awarded the Honeywell
    Scholarship for excellence at IIIT, Bangalore. {\period Jun 2006}
\end{category}


\end{document}
